\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-05-09 draft.tex
fix old typos in draft
fix A's probabilities and obj fcn

There are five players in the model. Each of three legislators faces a choice between the status quo, $x$ and a new policy proposal $s$. The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units. Note that legislators only have preferences about how they vote, not over which alternative wins.

@@

Given these assumptions, the probability that legislator $i$ votes against the new proposal is
	\[
					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a_i - b_i \leq 0 \right] = \Pr\left[\ve \leq \beta z - \alpha - a_i + b_i \right] 
	\]
Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$.	Whether a legislator $i$ votes ``no'' is a random variable, denote it $Q(i)$, distributed Bernoulli with this probability:
	\[
		Q(i) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha -a_i+ b_i \right)}}
	\]

For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$. Then $Y_B = \frac{\beta}{2} - \alpha - a_{-\frac{1}{2}} + b_{-\frac{1}{2}}$, $X_B = -\alpha - a_0+ b_0$ and $Z_B = -\frac{\beta}{2} - \alpha - a_{\frac{1}{2}} + b_{\frac{1}{2}}\label{page:sh}$ represent the net ideal points in terms of $B$'s probability of winning the issue. We can then write the probability that each of the legislators, respectively, votes against the new proposal as $\frac{1}{1+e^{-Y_B}}$, $\frac{1}{1+e^{-X_B}}$ and $\frac{1}{1+e^{-Z_B}}$.

Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes. So the net ideal points from her point of view---that is, in terms of her winning the issue---are $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$, $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$, and $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$ with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$. We can then write the probability that each of the legislators votes for the new proposal as $\frac{1}{1+e^{-Y_A}}$, $\frac{1}{1+e^{-X_A}}$ and $\frac{1}{1+e^{-Z_A}}$.

@@

\subsection{Vote Buyer A}
Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
			  \begin{multline}
			    \max_{a_{-\frac{1}{2}}, a_0, a_{\frac{1}{2}}} 
					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a_j .
					\label{eq:obja}
				\end{multline}

>>>>

There are five players in the model. Each of three legislators faces a choice between the status quo, $s$ and a new policy proposal $x$. The utility function of legislator $i$ is given by $v(i) = u_i(x) - u_i(s)$, which is measured in money units. Note that legislators only have preferences about how they vote, not over which alternative wins.

@@

Given these assumptions, the probability that legislator $i$ votes against the new proposal is
	\[
					\Pr\left[v(i)\leq 0 \right] = \Pr\left[\alpha -\beta i + \ve + a_i - b_i \leq 0 \right] = \Pr\left[\ve \leq \beta i - \alpha - a_i + b_i \right] 
	\]
Assuming $\ve \sim \text{Logistic} \ (0,1)$, the probability that legislator $z$ votes ``no'' is $\frac{1}{1+e^{-\left(\beta i - \alpha - a_i + b_i \right)}}$.	Whether a legislator $i$ votes ``no'' is a random variable, denote it $Q(i)$, distributed Bernoulli with this probability:
	\[
		Q(i) \sim \text{Bernoulli}(p(z)) \hskip.2in \text{where} \hskip.2in p(z) = \frac{1}{1+e^{-\left(\beta z - \alpha -a_i+ b_i \right)}}
	\]

For ease of exposition, for now take $i \in \left\{ -\frac{1}{2}, 0, \frac{1}{2} \right\}$. Let $Y_B = \frac{\beta}{2} - \alpha - a_{-\frac{1}{2}} + b_{-\frac{1}{2}}$, $X_B = -\alpha - a_0+ b_0$ and $Z_B = -\frac{\beta}{2} - \alpha - a_{\frac{1}{2}} + b_{\frac{1}{2}}\label{page:sh}$ represent the net ideal points in terms of $B$'s probability of winning the issue. We can then write the probability that each of the legislators, respectively, votes against the new proposal as $\frac{1}{1+e^{-Y_B}}$, $\frac{1}{1+e^{-X_B}}$ and $\frac{1}{1+e^{-Z_B}}$.

We would also like to write the probabilities that the legislators vote in line with Vote Buyer A. The probability that a legislator votes for the new proposal is the complement of the probability that she votes for the status quo. Since Vote Buyer $A$ must take into account that Vote Buyer $B$ will react to her choice of bribes, we write these probabilities as $\frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}}$, $\frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}}$ and $\frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}}$ with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$.

@@

\subsection{Vote Buyer A}
Vote buyer A's objective function is similar in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
			  \begin{multline}
			    \max_{a_{-\frac{1}{2}}, a_0, a_{\frac{1}{2}}} 
					W_A \biggl[ \frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}} \frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}} +
					\frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}} \frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}} + \\
					\frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}} \frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}} - 2	\frac{e^{-Z_B(\bm{a})}}{1+e^{-Z_B(\bm{a})}} \frac{e^{-X_B(\bm{a})}}{1+e^{-X_B(\bm{a})}} \frac{e^{-Y_B(\bm{a})}}{1+e^{-Y_B(\bm{a})}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a_j .
					\label{eq:obja}
				\end{multline}
